---
title: "CV Citation Badge Generator"
format: html
engine: knitr
---

## 1. Setup & Configuration

This section loads necessary libraries for both R and Python.

**Prerequisites:**

1.  **R Packages:** Run `install.packages(c("xml2", "httr", "jsonlite", "scholar", "reticulate", "tools"))` in your R console once.
2.  **Python Package:** Open your terminal and run `pip install docx2pdf`.
3.  **Microsoft Word:** Must be installed on your Mac.

```{r setup, message=FALSE, warning=FALSE}
# --- R Library Loading ---
library(xml2)
library(httr)
library(jsonlite)
library(scholar)
library(tools)
library(reticulate)

# --- USER CONFIGURATION ---
CV_SOURCE_PATH <- "/Users/seungjukim/Library/CloudStorage/GoogleDrive-seungju7@illinois.edu/My Drive/PERSONAL/CV/SK_cv.docx"
SCHOLAR_ID     <- "JWNJV9UAAAAJ"
OUTPUT_FOLDER  <- "_site/cv"

# Ensure output directory exists
if(!dir.exists(OUTPUT_FOLDER)) dir.create(OUTPUT_FOLDER, recursive = TRUE)

# Define paths for intermediate DOCX and final PDF
# We use absolute paths to ensure Python finds them easily
INTERMEDIATE_DOCX <- normalizePath(file.path(getwd(), OUTPUT_FOLDER, paste0(file_path_sans_ext(basename(CV_SOURCE_PATH)), "_BADGED.docx")), mustWork = FALSE)
FINAL_PDF         <- sub("\\.docx$", ".pdf", INTERMEDIATE_DOCX)

message("Source: ", CV_SOURCE_PATH)
message("Target: ", FINAL_PDF)
````

## 2\. Citation Data Fetching (R)

We use R to fetch citation counts because `scholar` and `httr` are robust for this task.

```{r fetch_data}
# --- Helper Functions ---

get_total_citations <- function(id) {
  message("📊 Fetching Google Scholar total...")
  tryCatch({
    get_profile(id)$total_cites
  }, error = function(e) { message("Error fetching Google Scholar: ", e$message); NA })
}

get_dimensions_citations <- function(doi) {
  # Dimensions API lookup
  url <- paste0("[https://metrics-api.dimensions.ai/doi/](https://metrics-api.dimensions.ai/doi/)", doi)
  tryCatch({
    res <- GET(url, add_headers(Accept = "application/json"), timeout(10))
    if (status_code(res) == 200) {
      fromJSON(content(res, "text", encoding = "UTF-8"))$times_cited
    } else { NA }
  }, error = function(e) { NA })
}

# --- Execution ---
total_cites <- get_total_citations(SCHOLAR_ID)
message("✅ Total Citations Found: ", total_cites)
```

## 3\. XML Processing (R)

This chunk performs the "surgery" on the DOCX file to insert the badges. We use a **safe ID strategy** (starting at 50,000) to ensure we never clash with Word's internal IDs.

```{r process_xml}
# 1. Setup Temp Directory
tmp_dir <- tempdir()
unzip_dir <- file.path(tmp_dir, "docx_unzipped")

# Clean previous runs
if(dir.exists(unzip_dir)) unlink(unzip_dir, recursive = TRUE)
dir.create(unzip_dir)

# 2. Unzip the DOCX
message("📝 Unzipping DOCX structure...")
unzip(CV_SOURCE_PATH, exdir = unzip_dir)

# 3. Read XML Files
doc_xml_path  <- file.path(unzip_dir, "word", "document.xml")
rels_xml_path <- file.path(unzip_dir, "word", "_rels", "document.xml.rels")

doc_xml  <- read_xml(doc_xml_path)
rels_xml <- read_xml(rels_xml_path)
ns       <- xml_ns(doc_xml)

# --- A. Update [[XX]] Placeholder ---
xx_nodes <- xml_find_all(doc_xml, "//w:t[contains(text(), '[[XX]]')]", ns)
if(length(xx_nodes) > 0) {
  xml_text(xx_nodes) <- gsub("\\[\\[XX\\]\\]", total_cites, xml_text(xx_nodes))
  message("✅ Updated [[XX]] placeholder -> ", total_cites)
}

# --- B. Insert Badges ---
badge_nodes <- xml_find_all(doc_xml, "//w:t[contains(text(), '[[ADD BADGE]]')]", ns)
message("🏷️  Found ", length(badge_nodes), " badge markers.")

if(length(badge_nodes) > 0) {
  # Start high to avoid collision with Word's internal rIds
  next_id <- 50000 
  
  for(node in badge_nodes) {
    # 1. Find DOI in the surrounding paragraph
    run_node <- xml_parent(node)
    p_node   <- xml_parent(run_node)
    p_text   <- xml_text(p_node)
    
    # Robust DOI Regex
    doi_match <- regmatches(p_text, gregexpr("10\\.\\d{4,}/[^\\s<>\\[\\]\"']+", p_text, perl=TRUE))[[1]]
    doi <- if(length(doi_match) > 0) gsub("[.,;:]+$", "", doi_match[1]) else NA
    
    # 2. Clear the marker text immediately
    xml_text(node) <- gsub("\\[\\[ADD BADGE\\]\\]", "", xml_text(node))
    
    if(!is.na(doi)) {
      message("   🔎 DOI: ", doi)
      cites <- get_dimensions_citations(doi)
      rid   <- paste0("rId", next_id)
      next_id <- next_id + 1
      
      # 3. Add Relationship (Link Target)
      xml_add_child(rels_xml, "Relationship", 
                    Id=rid, 
                    Type="[http://schemas.openxmlformats.org/officeDocument/2006/relationships/hyperlink](http://schemas.openxmlformats.org/officeDocument/2006/relationships/hyperlink)",
                    Target=paste0("[https://badge.dimensions.ai/details/doi/](https://badge.dimensions.ai/details/doi/)", doi),
                    TargetMode="External")
      
      # 4. Create Badge XML Node
      # We style manually (Blue/Underline) to avoid "Styles" corruption errors
      cite_str <- if(is.na(cites)) "0" else as.character(cites)
      
      badge_fragment <- paste0(
        '<w:hyperlink xmlns:w="[http://schemas.openxmlformats.org/wordprocessingml/2006/main](http://schemas.openxmlformats.org/wordprocessingml/2006/main)" ',
        'xmlns:r="[http://schemas.openxmlformats.org/officeDocument/2006/relationships](http://schemas.openxmlformats.org/officeDocument/2006/relationships)" r:id="', rid, '">',
        '<w:r>',
          '<w:rPr>',
            '<w:b/>',                   # Bold
            '<w:color w:val="0563C1"/>', # Standard Blue Link Color
            '<w:u w:val="single"/>',     # Underline
          '</w:rPr>',
          '<w:t xml:space="preserve">[Citation = ', cite_str, ']</w:t>',
        '</w:r>',
        '</w:hyperlink>'
      )
      
      # 5. Insert Sibling
      xml_add_sibling(run_node, read_xml(badge_fragment), .where="after")
      message("      ✅ Badge added: ", cite_str)
    } else {
      message("      ⚠️ No DOI found for this marker.")
    }
  }
}

# --- C. Save & Zip ---
message("💾 Saving XML modifications...")
write_xml(doc_xml, doc_xml_path)
write_xml(rels_xml, rels_xml_path)

# Correct file ordering for Word: [Content_Types].xml MUST be first
all_files <- list.files(unzip_dir, recursive = TRUE)
if("[Content_Types].xml" %in% all_files) {
  files_to_zip <- c("[Content_Types].xml", setdiff(all_files, "[Content_Types].xml"))
} else {
  files_to_zip <- all_files
}

# Create the intermediate DOCX
if(file.exists(INTERMEDIATE_DOCX)) unlink(INTERMEDIATE_DOCX)

old_wd <- getwd()
setwd(unzip_dir)
zip(INTERMEDIATE_DOCX, files_to_zip, flags = "-r9Xq")
setwd(old_wd)

message("📦 Intermediate DOCX ready: ", INTERMEDIATE_DOCX)
```

## 4\. PDF Conversion (Python)

We use Python's `docx2pdf` library here. This is cleaner than R because `docx2pdf` handles the complex AppleScript identifiers (like the integer `17` for PDF format) internally, preventing the errors we saw earlier.

```{python convert_pdf}
import sys
import os
try:
    from docx2pdf import convert
except ImportError:
    print("❌ Error: 'docx2pdf' not installed. Run 'pip install docx2pdf' in terminal.")
    sys.exit(1)

# Get paths passed from R
input_docx = r.INTERMEDIATE_DOCX
output_pdf = r.FINAL_PDF

print(f"🔄 Starting PDF Conversion...")
print(f"   Input:  {input_docx}")
print(f"   Output: {output_pdf}")

try:
    # Convert directly
    convert(input_docx, output_pdf)
    print("✅ Conversion Successful!")
except Exception as e:
    print(f"❌ Conversion Failed: {e}")
```

## 5\. Verification

Check if the file was actually created.

```{r verify}
if(file.exists(FINAL_PDF)) {
  message("🎉 FINAL SUCCESS! Your CV is ready.")
  message("📂 Location: ", FINAL_PDF)
  message("📏 Size: ", file.info(FINAL_PDF)$size, " bytes")
  
  # Optional: Open the file automatically
  system(paste("open", shQuote(FINAL_PDF)))
} else {
  warning("⚠️ PDF file was not created. Check Python chunk output above.")
}
```

