---
title: "Research"
date: last-modified
date-format: "MM/DD/YYYY"
author:
  - name: Seungju Kim
    orcid: 0009-0009-5166-9170
    email: seungju7@illinois.edu
    affiliation: 
      - name: University of Illinois, Urbana-Champaign
        department: Psychology
title-block-banner: false
format: html
comments: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| include: FALSE
# Required packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(scholar, rcrossref, dplyr, stringr, htmltools)
```

<a href="https://docs.google.com/document/d/1bB2WnhJIigiq-S9CmZNKPpmEYytFz98U/export?format=pdf" 
   class="btn btn-success" 
   target="_blank"
   id="cv-download-button"
   data-tracking="cv-download">
    <i class="bi bi-file-earmark-pdf"></i> Download CV
</a>
<span id="count" class="badge bg-primary ms-2">0</span>


<script type="module">
  import { initializeApp } from 'https://www.gstatic.com/firebasejs/9.6.1/firebase-app.js';
  import { getFirestore, doc, getDoc, runTransaction } from 'https://www.gstatic.com/firebasejs/9.6.1/firebase-firestore.js';

  document.addEventListener('DOMContentLoaded', function() {
    // Your web app's Firebase configuration
    const firebaseConfig = {
      apiKey: "{{ FB_API }}",
      authDomain: "cv-download-40a41.firebaseapp.com",
      projectId: "cv-download-40a41",
      storageBucket: "cv-download-40a41.firebasestorage.app",
      messagingSenderId: "842134969852",
      appId: "{{ APPID }}",
      measurementId: "G-7149VRMDP5"
    };

    // Initialize Firebase
    const app = initializeApp(firebaseConfig);
    const db = getFirestore(app);
    const countRef = doc(db, "counts", "cvDownload"); // Updated to match your new structure

    // Function to increment the CV download count
    async function incrementCount() {
      console.log("Increment button clicked");
      try {
        await runTransaction(db, async (transaction) => {
          const countDoc = await transaction.get(countRef);
          if (!countDoc.exists()) {
            console.log("Document does not exist. Creating new document.");
            transaction.set(countRef, { counts: 1 }); // Changed count to counts to match your field name
          } else {
            const newCount = countDoc.data().counts + 1; // Changed count to counts
            console.log("Document exists. Updating count to:", newCount);
            transaction.update(countRef, { counts: newCount }); // Changed count to counts
          }
        });
        console.log("Transaction successful!");
        getCount();
      } catch (error) {
        console.error("Transaction failed:", error);
      }
    }

    // Function to get the current CV download count
    async function getCount() {
      console.log("Fetching count from Firestore");
      try {
        const countDoc = await getDoc(countRef);
        if (countDoc.exists()) {
          console.log("Count document exists:", countDoc.data());
          document.getElementById("count").innerText = countDoc.data().counts; // Changed count to counts
        } else {
          console.log("Count document does not exist");
          document.getElementById("count").innerText = "0";
        }
      } catch (error) {
        console.error("Error getting document:", error);
      }
    }

    // Load the current count when the page loads
    getCount();

    // Attach event listener to the CV download button
    document.getElementById('cv-download-button').addEventListener('click', incrementCount);
  });
</script>

:::callout-note
All publications are free to access. Some files may not be accessible in their final forms due to copyright restrictions.

Please refer to the legend below:

{{< iconify ic:baseline-picture-as-pdf size=lg >}} PDF File

{{< iconify academicons:preregistered size=lg >}} Preregistration

{{< iconify academicons:osf-square size=lg >}} OSF Repository

{{< iconify academicons:psyarxiv size=lg >}} PsyArXiv Preprint
:::

## Publications

```{r publications, results='asis', echo=FALSE}
source("citations.R")
# Create citation list with your manually formatted citations
my_publications <- list(
  # Pub 1
  list(
    citation = 'Edwards, K. M., Littleton, H., Gardella, J., Wheeler, L. A., Farquhar-Leicester, A., Xu, W., Spitz, C., Hespe, P., Chavez, A., **Kim, S.,** Choi, D., Allen, M., Camp, E., Ashworth, S., Sharma, M., Girard, J., Higgins, M., Hopfauf, S., & Neighbors, C. (2025). An Online Program for Sexual and Gender Minority Youth Reduces Alcohol Use and Teen Dating Violence: A Randomized Controlled Trial. *Journal of Studies on Alcohol and Drugs.* [https://doi.org/10.15288/jsad.24-00007](doi.org/10.15288/jsad.24-00007)',
    doi = "10.15288/jsad.24-00007",
    pdf_link = "https://drive.google.com/file/d/1q02lGcU0Nf6Hj0mVu9Fl2wygBx3SfjlY/view?usp=sharing",
    preregistration_link = NULL,
    osf_link = NULL,
    preprint_link = NULL
  ),
  
  # Pub 2
  list(
    citation = '**Kim, S.,** Lefevor, G.T. & Skidmore, S.J. (2024). Mitigating the Impact of Religiously Based Family Expectations on Depression among Sexual and Gender Minorities: The Role of Authenticity. *Journal of Homosexuality.* [https://doi.org/10.1080/00918369.2024.2378745](https://doi.org/10.1080/00918369.2024.2378745)',
    doi = "10.1080/00918369.2024.2378745",
    pdf_link = "https://drive.google.com/file/d/1Vvemb89xpOLp8mjQS0HePneRliNTD5zF/view?usp=sharing",
    preregistration_link = NULL,
    osf_link = NULL,
    preprint_link = NULL
  ),
  
  # Pub 3
  list(
    citation = 'Lefevor, G.T., **Kim, S.,** & Perez-Figueroa, A.M. (2024). How does religiousness influence health among sexual and gender minorities? Evaluating the propositions of the religious/spiritual stress and resilience model. *Psychology of Sexual Orientation and Gender Diversity.* [https://doi.org/10.1037/sgd0000749](https://doi.org/10.1037/sgd0000749)',
    doi = "10.1037/sgd0000749",
    pdf_link = "https://drive.google.com/file/d/1qVH4TEqYISAWjoGsT96BUgfcmWyyhzrG/view?usp=sharing",
    preregistration_link = NULL,
    osf_link = NULL,
    preprint_link = NULL
  )
)

# Generate and display the publications table
cat(generate_publications_table(my_publications))
```

## Preprints

:::callout-warning
A preprint is an early-stage research paper not yet peer-reviewed or published in a scientific journal. Findings should be considered preliminary, may contain errors, and could change substantially in the final published version. While preprints promote rapid scientific exchange, they should not be cited as established scientific fact, reported as definitive in news media, or used to guide clinical decisions without appropriate context.
:::

```{r preprints, results='asis', echo=FALSE}
# You can create separate sections for different types of publications
preprints <- list(
  list(
    citation = "**Kim, S.,** & Xu, W. (2024). Religious Leaders' LGBQ Support: A National Survey Examining Psychosocial, Religious, and Congregational Factors. *OSF* [https://doi.org/10.31234/osf.io/rc8sh](https://doi.org/10.31234/osf.io/rc8sh)",
    doi = "10.31234/osf.io/rc8sh",
    pdf_link = NULL,
    preregistration_link = "https://osf.io/vy2bc?view_only=27e52b269f4d43f2b66275c3524becdf",
    osf_link = "https://osf.io/epdvu/?view_only=95aebd4a3ec940eb83eb198b8848c7d8",
    preprint_link = "https://doi.org/10.31234/osf.io/rc8sh"
  ),
  # Preprint 2
  list(
    citation = "**Kim, S.,** Wang, D. C., Gin, D. H. C., Deasy, J. A., & Sandage, S. (2024). Contrasting Experiences: Gender Disparities in Spirituality, Character Strengths, Mental Health, and Social Justice Among Next-Generation Religious Leaders. *OSF* [https://doi.org/10.31234/osf.io/mqwg9](https://doi.org/10.31234/osf.io/mqwg9)",
    doi = "10.31234/osf.io/mqwg9",
    pdf_link = NULL,
    preregistration_link = NULL,
    osf_link = NULL,
    preprint_link = "https://doi.org/10.31234/osf.io/mqwg9"
  ),
  # Preprint 3
  list(
    citation = "**Kim, S.,** Jankowski, P., Hawkins, H.A., & Wang, D.C. (2024). Patterns of Christian Nationalist Engagement and Connections to Spirituality. *OSF* [https://doi.org/10.31234/osf.io/9xt8r](https://doi.org/10.31234/osf.io/9xt8r)",
    doi = "10.31234/osf.io/9xt8r",
    pdf_link = NULL,
    preregistration_link = NULL,
    osf_link = NULL,
    preprint_link = "https://doi.org/10.31234/osf.io/9xt8r"
  )
)

# Generate and display the preprints table
cat(generate_publications_table(preprints))
```

