---
title: "Research"
author:
  - name: Seungju Kim
    orcid: 0009-0009-5166-9170
    email: seungju7@illinois.edu
    affiliation: 
      - name: University of Illinois, Urbana-Champaign
        department: Psychology
title-block-banner: false
format: html
comments: false
description: "" 
listing:
  - id: published
    include: 
      type: "Published"
    contents: papers.yaml
    template: papers.ejs
    filter-ui: false
    sort: "date desc"
    sort-ui: false
  - id: preprints
    include: 
      type: "Preprint"
    contents: papers.yaml
    template: papers.ejs
    sort: "date desc" 
    sort-ui: false
toc: true    
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| include: FALSE
if (!require("pacman")) install.packages("pacman")
pacman::p_load(scholar, rcrossref, dplyr, stringr, htmltools, here, tidyverse, ggiraph, patchwork, gdtools, gfonts)
register_gfont("Inter")
```

<div style="display:flex;align-items:center;flex-wrap:wrap;gap:0.5rem;">
<button class="btn btn-success" id="cv-download-trigger" style="cursor:pointer;"><i class="bi bi-file-earmark-pdf"></i> Download CV</button>
<span id="count" class="badge bg-primary">0</span>
</div>
<div id="turnstile-container" style="display:none;margin-top:0.5rem;"></div>
<p id="ts-status" style="font-size:0.875rem;margin-top:0.25rem;min-height:1.2em;"></p>

<!-- Turnstile globals: plain script so onTurnstileLoad is reachable -->
<script>
  window._tsScriptLoaded = false;
  window._tsWidgetId     = null;
  function onTurnstileLoad() { window._tsScriptLoaded = true; }
</script>
<script src="https://challenges.cloudflare.com/turnstile/v0/api.js?render=explicit&onload=onTurnstileLoad" defer></script>

<script type="module">
  import { initializeApp } from 'https://www.gstatic.com/firebasejs/9.6.1/firebase-app.js';
  import { getFirestore, doc, getDoc, runTransaction } from 'https://www.gstatic.com/firebasejs/9.6.1/firebase-firestore.js';

  document.addEventListener('DOMContentLoaded', function() {
    const firebaseConfig = {
      apiKey: "{{ FB_API }}",
      authDomain: "cv-download-40a41.firebaseapp.com",
      projectId: "cv-download-40a41",
      storageBucket: "cv-download-40a41.firebasestorage.app",
      messagingSenderId: "842134969852",
      appId: "{{ APPID }}",
      measurementId: "G-7149VRMDP5"
    };

    const WORKER_URL = 'https://turnstile-verify.follhim.workers.dev';

    const app = initializeApp(firebaseConfig);
    const db  = getFirestore(app);
    const countRef = doc(db, "counts", "cvDownload");

    async function incrementCount() {
      try {
        await runTransaction(db, async (transaction) => {
          const countDoc = await transaction.get(countRef);
          if (!countDoc.exists()) {
            transaction.set(countRef, { counts: 1 });
          } else {
            transaction.update(countRef, { counts: countDoc.data().counts + 1 });
          }
        });
        getCount();
      } catch (error) {
        console.error("Transaction failed:", error);
      }
    }

    async function getCount() {
      try {
        const countDoc = await getDoc(countRef);
        document.getElementById("count").innerText =
          countDoc.exists() ? countDoc.data().counts : "0";
      } catch (error) {
        console.error("Error getting document:", error);
      }
    }

    async function verifyWithWorker(token) {
      try {
        const res = await fetch(`${WORKER_URL}/verify`, {
          method:  'POST',
          headers: { 'Content-Type': 'application/json' },
          body:    JSON.stringify({ token })
        });
        console.log('HTTP status:', res.status);
        const data = await res.json();
        console.log('Worker response:', JSON.stringify(data));
        return data;
      } catch (err) {
        console.error('Worker verification error:', err);
        return { success: false };
      }
    }

    function navigateTo(url) {
      window.location.href = url;
    }

    const container = document.getElementById('turnstile-container');
    const status    = document.getElementById('ts-status');

    function renderWidget() {
      if (window._tsWidgetId !== null) return;

      container.style.display = 'block';
      status.textContent = '';

      window._tsWidgetId = turnstile.render('#turnstile-container', {
        sitekey:    '0x4AAAAAADNayBUca6pR_5fG',
        execution:  'render',
        appearance: 'always',
        callback: async function(token) {
          status.textContent = 'Opening your CV…';
          const data = await verifyWithWorker(token);
          console.log('data.success:', data.success);
          console.log('data.token:', data.token);
          if (data.success && data.token) {
            await incrementCount();
            navigateTo(`${WORKER_URL}/redeem?token=${data.token}`);
            container.style.display = 'none';
            status.textContent = '';
            turnstile.remove(window._tsWidgetId);
            window._tsWidgetId = null;
          } else {
            status.textContent = 'Verification failed — please try again.';
            console.error('Verification failed. Full response:', JSON.stringify(data));
            turnstile.remove(window._tsWidgetId);
            window._tsWidgetId = null;
          }
        },
        'error-callback': function() {
          status.textContent = 'Verification error — please try again.';
          turnstile.remove(window._tsWidgetId);
          window._tsWidgetId = null;
        },
        'expired-callback': function() {
          turnstile.remove(window._tsWidgetId);
          window._tsWidgetId = null;
        }
      });
    }

    getCount();

    document.getElementById('cv-download-trigger').addEventListener('click', function() {
      if (!window._tsScriptLoaded) {
        status.textContent = 'Still loading — please try again in a moment.';
        return;
      }
      renderWidget();
    });
  });
</script>

```{r}
#| echo: FALSE
#| warning: FALSE
#| asis: TRUE
pacman::p_load(httr, jsonlite, tidyverse, ggiraph, patchwork, here)

scholar_id <- "JWNJV9UAAAAJ"

cache_dir <- here("_data_cache")
if (!dir.exists(cache_dir)) dir.create(cache_dir, recursive = TRUE)

save_cache <- function(data, name) {
  saveRDS(data, file.path(cache_dir, paste0(name, ".rds")))
}

load_cache <- function(name) {
  path <- file.path(cache_dir, paste0(name, ".rds"))
  if (file.exists(path)) readRDS(path) else NULL
}

get_citation_history_serpapi <- function(scholar_id, api_key) {
  url <- "https://serpapi.com/search.json"
  response <- GET(url, query = list(
    engine = "google_scholar_author",
    author_id = scholar_id,
    api_key = api_key
  ))
  if (status_code(response) == 200) {
    data <- fromJSON(content(response, "text"))
    if ("cited_by" %in% names(data) && "graph" %in% names(data$cited_by)) {
      citation_graph <- data$cited_by$graph
      return(data.frame(
        year = as.numeric(citation_graph$year),
        cites = as.numeric(citation_graph$citations)
      ))
    }
  }
  return(NULL)
}

get_publications_serpapi <- function(scholar_id, api_key) {
  url <- "https://serpapi.com/search.json"
  response <- GET(url, query = list(
    engine = "google_scholar_author",
    author_id = scholar_id,
    api_key = api_key,
    view_op = "list_works",
    num = 100
  ))
  if (status_code(response) == 200) {
    data <- fromJSON(content(response, "text"))
    if ("articles" %in% names(data)) {
      publications <- data$articles
      if (nrow(publications) > 0 && "year" %in% names(publications)) {
        return(publications %>% filter(!is.na(year)) %>% count(year, name = "publications"))
      }
    }
  }
  return(NULL)
}

api_key <- Sys.getenv("SERPAPI_KEY")
if (api_key == "") stop("SERPAPI_KEY not found in environment variables.")

citation_data <- tryCatch({
  result <- get_citation_history_serpapi(scholar_id, api_key)
  if (!is.null(result)) save_cache(result, "citation_data")
  result
}, error = function(e) { message("Error: ", e$message); NULL })

if (is.null(citation_data)) {
  citation_data <- load_cache("citation_data")
  if (is.null(citation_data)) stop("No citation data available.")
}

publication_data <- tryCatch({
  result <- get_publications_serpapi(scholar_id, api_key)
  if (!is.null(result)) save_cache(result, "publication_data")
  result
}, error = function(e) { message("Error: ", e$message); NULL })

if (is.null(publication_data)) {
  publication_data <- load_cache("publication_data")
  if (is.null(publication_data)) stop("No publication data available.")
}

total_citations <- sum(citation_data$cites)
total_publications <- sum(publication_data$publications)

citations_plot <- citation_data %>%
  ggplot(aes(x = cites, y = as.factor(year))) +
  geom_col_interactive(aes(tooltip = cites), fill = "#4A90A4", width = 0.7) +
  labs(title = "Citation History Over Time", subtitle = paste("Total Citations:", total_citations),
       x = "# of Citations", y = "Year") +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "#0E2638", color = NA),
    panel.background = element_rect(fill = "#0E2638", color = NA),
    plot.title = element_text(size = 14, face = "bold", color = "#EBEBEB", family = "Helvetica"),
    plot.subtitle = element_text(size = 12, color = "#EBEBEB", family = "Helvetica"),
    axis.title = element_text(size = 12, color = "#EBEBEB", family = "Helvetica"),
    axis.text = element_text(size = 10, color = "#EBEBEB", family = "Helvetica"),
    axis.line = element_line(color = "#EBEBEB", size = 0.5),
    panel.grid.major = element_blank(), panel.grid.minor = element_blank()
  )

publications_plot <- publication_data %>%
  ggplot(aes(x = publications, y = as.factor(year))) +
  geom_col_interactive(aes(tooltip = publications), fill = "#7FB069", width = 0.7) +
  labs(title = "Publications Over Time", subtitle = paste("Total Publications:", total_publications),
       x = "# of Publications", y = "Year") +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "#0E2638", color = NA),
    panel.background = element_rect(fill = "#0E2638", color = NA),
    plot.title = element_text(size = 14, face = "bold", color = "#EBEBEB", family = "Helvetica"),
    plot.subtitle = element_text(size = 12, color = "#EBEBEB", family = "Helvetica"),
    axis.title = element_text(size = 12, color = "#EBEBEB", family = "Helvetica"),
    axis.text = element_text(size = 10, color = "#EBEBEB", family = "Helvetica"),
    axis.line = element_line(color = "#EBEBEB", size = 0.5),
    panel.grid.major = element_blank(), panel.grid.minor = element_blank()
  )

combined_plot <- citations_plot + publications_plot +
  plot_layout(ncol = 2) +
  plot_annotation(
    caption = paste("Data from Google Scholar via SerpApi (", Sys.Date(), ")", sep = ""),
    theme = theme(
      plot.background = element_rect(fill = "#0E2638", color = NA),
      plot.caption = element_text(size = 10, color = "#EBEBEB", family = "Helvetica")
    )
  )

girafe(ggobj = combined_plot, width_svg = 12, height_svg = 5, fonts = list(sans = "Helvetica"))
```

## Published Papers

:::{#published}
:::

## Preprints
:::callout-warning
A preprint is an early-stage research paper not yet peer-reviewed or published in a scientific journal. Findings should be considered preliminary, may contain errors, and could change substantially in the final published version. While preprints promote rapid scientific exchange, they should not be cited as established scientific fact, reported as definitive in news media, or used to guide clinical decisions without appropriate context.
:::

:::{#preprints}
:::